FMA: A Dataset For Music Analysis

### 2017-03-22 fma.tex
authorship

\oneauthor
{Kirell Benzi, \hspace{.2cm} Michaël Defferrard, \hspace{.2cm} Pierre Vandergheynst, \hspace{.2cm} Xavier Bresson}
 {{\tt michael.defferrard@epfl.ch, kirell.benzi@epfl.ch} \\
  {\tt pierre.vandergheynst@epfl.ch, xavier.bresson@epfl.ch} \\
  LTS2, EPFL, Lausanne, Switzerland}

>>>>

\oneauthor
{Michaël Defferrard, \hspace{.2cm} Kirell Benzi, \hspace{.2cm} Pierre Vandergheynst, \hspace{.2cm} Xavier Bresson}
 {{\tt michael.defferrard@epfl.ch, kirell.benzi@epfl.ch} \\
  {\tt pierre.vandergheynst@epfl.ch, xavier.bresson@epfl.ch} \\
  LTS2, EPFL, Lausanne, Switzerland}
